Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-21 xrb2/paper.tex
add citation

The {\tt F500} and {\tt F1000} runs both qualitatively resemble the flame structure in 
\citet{flame_wave1} --- a laterally propagating flame that is lifted off of the bottom of the fuel 
layer --- but they differ in their burning structures. Figures~\ref{fig:time_series_500} and 
\ref{fig:time_series_1000} show time series of the mean molecular weight, $\bar{A}$, for the {\tt 
F500} and {\tt F1000} runs.  Compared to those in \cite{flame_wave1}, ashes behind the flame do not 
reach as high atomic weights. This is not surprising, since those previous runs artificially 
boosted the reaction rates.  Comparing these two new runs, the burning is much more evolved for the 
higher rotation rate, and the ash is actually able to move ahead of the flame front (visible in the 
Figure  \ref{fig:time_series_1000} $100~\mathrm{ms}$ snapshot). We believe that this is because the increased 
rotation better confines the initial perturbation and subsequent expansion from the burning, 
increasing the temperature and density in the flame front such that the reaction rate increases, 
which allows the reactions to progress further. The $\dot{e}_\mathrm{nuc}$ plots in Figure 
\ref{fig:time_series_enuc_1000} also support this interpretation, with the interior of the 
flame nearest to the crust in the {\tt F1000} run reaching higher $\dot{e}_\mathrm{nuc}$ values 
than for the {\tt F500} run in Figure \ref{fig:time_series_enuc_500}. In contrast to {\tt F500} 
and {\tt F1000}, the lowest rotation run --- {\tt F250} --- failed to ignite. The lack of ignition 
for {\tt F250} also aligns with the reasoning given above, with the lower rotation in this case 
potentially leading to insufficient confinement such that the temperature and density required for 
ignition is not achieved. In this scenario, another source of confinement (e.g.\ magnetic fields) 
would need to take over at lower rotation rates to allow a burst to occur, at least for the initial 
model used here.

>>>>

The {\tt F500} and {\tt F1000} runs both qualitatively resemble the flame structure in 
\citet{flame_wave1} --- a laterally propagating flame that is lifted off of the bottom of the fuel 
layer --- but they differ in their burning structures. Figures~\ref{fig:time_series_500} and 
\ref{fig:time_series_1000} show time series of the mean molecular weight, $\bar{A}$, for the {\tt 
F500} and {\tt F1000} runs.  Compared to those in \cite{flame_wave1}, ashes behind the flame do not 
reach as high atomic weights. This is not surprising, since those previous runs artificially 
boosted the reaction rates.  Comparing these two new runs, the burning is much more evolved for the 
higher rotation rate, and the ash is actually able to move ahead of the flame front (visible in the 
Figure  \ref{fig:time_series_1000} $100~\mathrm{ms}$ snapshot). We believe that this is because the increased 
rotation better confines the initial perturbation and subsequent expansion from the burning, 
increasing the temperature and density in the flame front such that the reaction rate increases, 
which allows the reactions to progress further. The $\dot{e}_\mathrm{nuc}$ plots in Figure 
\ref{fig:time_series_enuc_1000} also support this interpretation, with the interior of the 
flame nearest to the crust in the {\tt F1000} run reaching higher $\dot{e}_\mathrm{nuc}$ values 
than for the {\tt F500} run in Figure \ref{fig:time_series_enuc_500}. In contrast to {\tt F500} 
and {\tt F1000}, the lowest rotation run --- {\tt F250} --- failed to ignite. The lack of ignition 
for {\tt F250} also aligns with the reasoning given above, with the lower rotation in this case 
potentially leading to insufficient confinement such that the temperature and density required for 
ignition is not achieved. In this scenario, another source of confinement (e.g.\ magnetic fields, see \citep{art-2016-cavecchi-etal}) 
would need to take over at lower rotation rates to allow a burst to occur, at least for the initial 
model used here.
